Generalized Bradley-Terry models

### 2025-04-02 inst/jss_hyper3_real.Rnw
typos

<<testlambdazero, cache = TRUE, eval = TRUE, echo = FALSE, fig = TRUE>>=
jj <- optimize(f = function(D){f(c(lambda=1, D))}, interval = c(0.1, 0.4), maximum = TRUE)
@
%
Further, we may calculate a support function over the
$(\lambda,D)$-plane, shown in Figure~\ref{contourlambdaD}.  For
example, we may test the hypothesis that $\lambda=1$ [corresponding to
  the left hand side of Figure~\ref{contourlambdaD}] for which the
support is about \Sexpr{round(f(maxv)-jj$objective,2)}, far
exceeding the two units of support per degree of freedom
criteron~\citep{edwards1992}.  Alternatively, we can observe that this
lies in the tail region of its asymptotic null $\chi^2_2$ distribution
with a $p$~value of about \Sexpr{signif(pchisq(f(maxv)-jj$objective,lower.tail=FALSE,df=2),digits=2)}.

@@

\begin{figure}[htbp]
  \begin{center}
<<csgo_plotlikelam, echo=FALSE>>=
plot(log(lam), L - max(L), type='b')
segments(x0 = log(csgo_optlam),y0 = -0.5, y1 =  0.1, col = 'red')
segments(x0 = log(csgo_lower), y0 = -2.2, y1 = -1.8, col = 'blue')
segments(x0 = log(csgo_upper), y0 = -2.2, y1 = -1.8, col = 'blue')
abline(v = 0, col = 'gray')
abline(h = c(0, -2), col = 'gray')
@ 
\caption{A\label{profsupcounterstrike} profile support function for
  the red bus-blue bus parameter $\log\lambda$ applied to mutually
  supporting equivalence class
  $\left\lbrace\mbox{\skad},\mbox{\stew}\right\rbrace$.  Vertical gray
  line shows $H_0\colon\lambda =1$, for which the support is about
  $\Sexpr{round(csgo_support,2)}$ relative to the evaluate
  $\hat{\lambda}\simeq\Sexpr{round(csgo_optlam,3)}$ (small red bar),
  corresponding to a $p$~value of about
  $\Sexpr{round(csgo_pvalue,3)}$.  Horizontal lines show the
  two-units-of-support credible interval of
  $(\Sexpr{round(csgo_lower,3)},\Sexpr{round(csgo_upper,3)})$, marked
  in blue}
\end{center}
\end{figure}

>>>>

<<testlambdazero, cache = TRUE, eval = TRUE, echo = FALSE>>=
jj <- optimize(f = function(D){f(c(lambda=1, D))}, interval = c(0.1, 0.4), maximum = TRUE)
@
%
Further, we may calculate a support function over the
$(\lambda,D)$-plane, shown in Figure~\ref{contourlambdaD}.  For
example, we may test the hypothesis that $\lambda=1$ [corresponding to
  the left hand side of Figure~\ref{contourlambdaD}] for which the
support is about \Sexpr{round(f(maxv)-jj$objective,2)}, far
exceeding the two units of support per degree of freedom
criteron~\citep{edwards1992}.  Alternatively, we can observe that this
lies in the tail region of its asymptotic null $\chi^2_2$ distribution
with a $p$~value of about \Sexpr{signif(pchisq(f(maxv)-jj$objective,lower.tail=FALSE,df=2),digits=2)}.

@@

\begin{figure}[htbp]
  \begin{center}
<<csgo_plotlikelam, echo = FALSE, fig = TRUE>>=
plot(log(lam), L - max(L), type='b')
segments(x0 = log(csgo_optlam),y0 = -0.5, y1 =  0.1, col = 'red')
segments(x0 = log(csgo_lower), y0 = -2.2, y1 = -1.8, col = 'blue')
segments(x0 = log(csgo_upper), y0 = -2.2, y1 = -1.8, col = 'blue')
abline(v = 0, col = 'gray')
abline(h = c(0, -2), col = 'gray')
@ 
\caption{A\label{profsupcounterstrike} profile support function for
  the red bus-blue bus parameter $\log\lambda$ applied to mutually
  supporting equivalence class
  $\left\lbrace\mbox{\skad},\mbox{\stew}\right\rbrace$.  Vertical gray
  line shows $H_0\colon\lambda =1$, for which the support is about
  $\Sexpr{round(csgo_support,2)}$ relative to the evaluate
  $\hat{\lambda}\simeq\Sexpr{round(csgo_optlam,3)}$ (small red bar),
  corresponding to a $p$~value of about
  $\Sexpr{round(csgo_pvalue,3)}$.  Horizontal lines show the
  two-units-of-support credible interval of
  $(\Sexpr{round(csgo_lower,3)},\Sexpr{round(csgo_upper,3)})$, marked
  in blue}
\end{center}
\end{figure}
